Quasars Probing Quasars IX. The Kinematics of the Circumgalactic Medium Surrounding $z\sim2$ Quasars [v1.4]

### 2017-03-03 QPQ9/qpq9_draft.tex
draft version 1.4

\title{Quasars Probing Quasars IX. Probing the Circumgalactic Flows of Quasars [v1.4]}

@@

\begin{abstract}
Absorption-line analysis of the circumgalactic medium has traditionally been limited by the 
difficulty to distinguish between inflows and outflows. We examine the flows of gas in the 
environments of massive galaxies hosting quasars at $z\sim2$. We employ 115 projected quasar pairs 
to study the circumgalactic gas of the foreground quasars in absorption. The foreground quasars 
have precise redshift measurements with uncertainty $<400\,{\rm km\,s^{-1}}$. We stack the 
background quasar spectra at the foreground quasar's systemic redshift. The mean absorption in 
\ion{C}{2}, \ion{C}{4}, and \ion{Mg}{2} show large velocity widths, and have velocity 
centroids that show a small positive offset relative to the systemic. We argue that a possible 
explanation to the observed velocity fields is outflowing gas combined with anisotropic or 
intermittent ionizing radiation of the quasars. 
\end{abstract}

@@

\section{Introduction}
\label{sec:introduction}
%\begin{itemize}
%\item Flows
%\item Mass (Kaiser, Schaye)
%\item Directionality/symmetry
%\item Break the symmetry
%\end{itemize}

Galaxy formation and evolution are driven by the flows into and out of their interstellar medium. 
Current theories demand that star-forming galaxies maintain these flows. Gas accretes, cools, and 
adds to the fuel supply, while star formation feedback heats gas, blows it out of galaxies, and 
regulates star formation \citep[for a review see][]{SomervilleDave15}.

Direction observations of galactic flows are difficult to acquire. Detecting the presence of 
the gas is itself challenging. Either the gas mass is too small, or the gas density is too low for 
the detection of line-emission, e.g.\ 21\,cm, Ly$\alpha$, or H$\alpha$ from \ion{H}{1}. Resolving 
the kinematics and establishing the mass flux pose an even greater challenge. These challenges are 
accentuated for distant, young galaxies, where flows are predicted to prevail 
\citep{Keres+09,Fumagalli+11}. Therefore, with rare exceptions, 
\citep[e.g.][]{Cantalupo+14,Hennawi+15}, the community has relied on absorption-line spectroscopy 
to detect and characterize the gas surrounding galaxies 
\citep[e.g.][]{BergeronBoisse91,Steidel+10,Prochaska+11,Tumlinson+13}. With this 
experiment, researchers have had success in characterizing the large-scale flows around 
star-forming galaxies to reveal a net inflow, or a Kaiser effect for gas \citep{Rakic+12}.

A significant limitation of absorption-line analysis, especially regarding galactic flows, 
is the inherent symmetry of the experiment. One generally lacks any constraint on the distance of 
the gas along the sightline. Positive or negative velocities with respect to the galaxy may be 
interpreted as gas flowing either toward or away from the system. ``Down-the-barrel'' observations 
break this symmetry, and have generally provided evidence for flows away from galaxies 
\citep{Rupke+05,Martin05,Weiner+09,Rubin+14}. However, these data are frequently at low spectral 
resolution which limits one's sensitivity to inflowing gas.

In this paper (hereafter QPQ9), we examine the flows of gas in the environments of massive 
galaxies hosting quasars. Our approach leverages a large dataset of quasar pairs 
\citep[][QPQ1]{QPQ1} to use the 
standard technique of absorption-line spectroscopy with background quasars. These quasar pairs 
have angular separations that correspond to less than 300\,kpc projected separation at the 
foreground quasar's redshift. Our previous publications from these quasar pairs have established 
that these galaxies are surrounded by a massive, cool, and enriched circumgalactic medium 
\citep[QPQ5, QPQ6, QPQ7:][]{QPQ5,QPQ6,QPQ7}. We have collected a sample of 115 background 
spectra that are paired with foreground quasars with precisely measured redshifts. Our primary 
scientific interests are twofold: (i) search for signatures of galactic-scale outflows from the 
central galaxy, presumably driven by recent star formation and/or active galactic nuclei feedback; 
(ii) characterize the dynamics of galactic flows around these massive system. We further describe 
an aspect of this experiment that offers a unique opportunity to study galactic flows: we argue 
that, the anisotropic or intermittent radiation of the foreground quasars breaks the symmetry in 
the velocity field of circumgalactic absorbers.

Among the sightlines in the QPQ9 sample, 13 have spectral resolution $> 5000$ from echellette or 
echelle observations, and have been analyzed separately in QPQ8 \citep{QPQ8}. We measured the 
velocity field for \ion{C}{2}\,1334 and \ion{C}{4}\,1548, finding that the CGM frequently exhibits 
large flows that are offset from the systemic redshift. The offsets, $\delta v$, are often 
positive, with the sign convention that positive velocities are flowing away from the observer. 
From a sample of 7 \ion{C}{2} systems and 10 \ion{C}{4} systems, we measured the velocity 
interval that encompasses 90\% of the total optical depth, $\Delta v_{90}$, and the $1\sigma$ 
dispersion relative to the profile centroid, $\sigma_v$. The median $\Delta v_{90}$ is 
$555\,{\rm km\,s^{-1}}$ for \ion{C}{2}\,1334 and is $342\,{\rm km\,s^{-1}}$ for \ion{C}{4}\,1548. 
The median $\sigma_v$ is $249\,{\rm km\,s^{-1}}$ for \ion{C}{2}\,1334 and is 
$495\,{\rm km\,s^{-1}}$ for \ion{C}{4}\,1548. These velocity fields exceed all previous 
measurements from galaxies and/or absorption systems at any epoch.

@@

From our QPQ survey\footnote{http://www.qpqsurvey.org}, we have analyzed a subset of systems that 
pass within transverse separation $R_\perp<300$\,kpc from a foreground quasar with 
$z_{\rm fg} > 1.6$. We restrict the sample to foreground quasars with redshift measured from 
\ion{Mg}{2}\,2800, [\ion{O}{3}]\,5007, H$\alpha$, or H$\beta$ emission, giving a precision of 
$400\,{\rm km\,s^{-1}}$ or better. 
[\ion{O}{3}] emission-line redshifts have the smallest dispersion of $44\,{\rm km\,s^{-1}}$ about 
the systemic redshift, and we analyze the sub-sample with [\ion{O}{3}] redshifts separately. 
The [\ion{O}{3}] line has an average blueshift of $27\,{\rm km\,s^{-1}}$ about the systemic 
redshift \citep{Boroson05}, which has been added when we compute the 
redshift of the line. Systemic redshifts measured from \ion{Mg}{2} have a precision of 
$272\,{\rm km\,s^{-1}}$, and we have taken into account the median redshift of 
$97\,{\rm km\,s^{-1}}$ of \ion{Mg}{2} from [\ion{O}{3}] \citep{Richards+02}. In QPQ8 
\citep{QPQ8}, we have quantified the precision of H$\alpha$ and H$\beta$ to be 
$300\,{\rm km\,s^{-1}}$ and $392\,{\rm km\,s^{-1}}$ respectively. We further add to the QPQ 
dataset with quasar pairs selected from the public dataset of 
igmspec\footnote{https://github.com/specdb/igmspec}, which includes the spectra from the quasar 
catalogs based upon the Sloan Digital Sky Survey Seventh Data Release \citep{Schneider+10} and the 
Twelfth Data Release \citep{Paris+17}. We 
only select pairs with $z_{\rm fg}$ measured by \cite{HewettWild10} using the \ion{Mg}{2}\,1800 
emission-line. We reached a final sample size of 115. Figure~\ref{fig:experiment} summarizes the 
experimental design. We refer the reader to previous QPQ publications for the details on the 
redshift centroiding algorithm, data reduction, and continuum normalization (QPQ6; QPQ8).

@@

Table~\ref{tab:sample} lists the full QPQ9 sample. 
In Table~\ref{tab:summary}, we list the sample size, the median $z_{\rm fg}$, and the median 
$R_\perp$ of the quasar pairs that survive the above selection criteria for \ion{C}{2}\,1334, 
\ion{C}{4}\,1548, and \ion{Mg}{2}\,2796 respectively. In Table~\ref{tab:summary_OIII}, we provide 
the summary for the sub-sample with $z_{\rm fg}$ measured from [\ion{O}{3}].

@@

@@

We create composite spectra that average over the intrinsic scatter in quasar environments, 
continuum placement errors, and redshift errors. The individual spectra of background quasars are 
shifted to the rest-frame of the foreground quasars at the transitions of interest. Each spectrum 
has been linearly interpolated onto a fixed velocity grid centered at $z_{\rm fg}$ with bins of 
$100\,{\rm km\,s^{-1}}$. For a velocity bin of this size, it is unncessary to smooth the data to a 
common spectral resolution. The individual spectra are then combined with a mean or a median 
statistic. Bad pixels in the individual spectra have been masked before generating the 
composites. Since each quasar pair gives an independent probe of the CGM, each pair has an equal 
weighting in the stacked profiles, i.e.\ we do not weight the spectra by the measured S/N near the 
metal ion transitions. Scatter in the stacked spectra is dominated by randomness in the CGM rather 
than error sources. The mean statistic of the individual spectra yields a good estimate of the 
average absorption and preserves equivalent width. The median statistic is less sensitive to 
outliers, however the averaged equivalent width is smaller and the analysis on the velocity field 
becomes more uncertain. In the following we present stacked spectra using both the mean and the 
median statistic.

%[Update the mean and scatter of emission-line redshifts relative to systemic to Shen+16?]

In Figure~\ref{fig:stacks_and_fits}, we present mean and median stacks of \ion{C}{2}\,1334, 
\ion{C}{4}\,1548, and \ion{Mg}{2}\,2796 absorption of the QPQ9 sample. We focus on the 
analysis results of the \ion{C}{2} mean stack. \ion{C}{4} and \ion{Mg}{2} are doublet transitions 
and it is more challenging to interpret their kinematics, while the median stacks have smaller 
equivalent widths.

%To assess the average absorption of these transitions,
%we have combined the data with a novel technique.
%We have fitted the combined dataset using a cubic b-spline
%with knots at every 100\,kms.  We weighted each data
%point by the velocity width of the pixel to insure that 
%each sightline makes an equal contribution to the stack.
%These b-spline profiles are presented in the figure
%and a trivial integration gives the reported equivalent
%widths.
%[consider down-weighting systems with $<3\sigma$ EW]
%[Comnent on EW from 'standard' technique]

Two results are evident in Figure~\ref{fig:stacks_and_fits}: (i) the mean \ion{C}{2} stack 
exhibits excess absorption spanning a large velocity width; (ii) the mean absorption is skewed 
toward positive velocities. To model the absorption, we introduce a Gaussian profile while 
allowing a constant pseudo-continuum level to vary. We perform $\chi^2$ minimization with each 
channel by equal weight. From the best-fit to the data, we measure the centroid of the \ion{C}{2} 
stack to be $+170\,{\rm km\,s^{-1}}$ and the $1\sigma$ dispersion to be $388\,{\rm km\,s^{-1}}$. 
The centroid suggests an asymmetry that contradicts the standard expectation, while the dispersion 
suggests extreme kinematics. The median stack, on the other hand, shows weaker absorption, and the 
Gaussian model has a centroid closer to zero.

We also create mean and median stack for the sub-sample with [\ion{O}{3}] redshifts and model the 
absorption with Gaussian best-fit. The \ion{C}{2} mean stack for this sub-sample has a centroid at 
$+207\,{\rm km\,s^{-1}}$, and a dispersion of $355\,{\rm km\,s^{-1}}$, consistent with the full 
sample.

@@

The above analyses are summarized in Table~\ref{tab:summary} and Table~\ref{tab:summary_OIII}. The 
Gaussian models normalized to pseudo-continuum are overplotted on the data stacks in 
Figure~\ref{fig:stacks_and_fits}.

\input{Tables/tab_summ.tex}
%\input{tab_summ.tex}
\input{Tables/tab_summ_OIII.tex}
%\input{tab_summ_OIII.tex}

\begin{figure}
\includegraphics[width=2.5in]{Figures/fig_stack_z1.pdf}
%\includegraphics[width=2.5in]{f03.pdf}
\caption{Mean stack at \ion{Mg}{2}\,2796, for a lower redshift sample of quasar pairs at 
$z\sim0.9$. Line-style coding is the same as in Figure~\ref{fig:stacks_and_fits}. The centroid is 
approximately $0\,{\rm \,km\,s^{-1}}$, and the absorption is weaker than the main QPQ9 sample. 
}
\label{fig:stack_z1}
\end{figure}

\begin{figure}
\includegraphics[width=3.4in]{Figures/fig_stacks_fg.pdf}
%\includegraphics[width=3.4in]{f04.pdf}
\caption{Mean stacks of the foreground quasar spectra at \ion{C}{2}\,1334, \ion{C}{4}\,1548, and 
\ion{Mg}{2}\,2796 for the QPQ9 sample. For \ion{C}{2} and \ion{Mg}{2}, there is no evidence of 
excess absorption near $z_{\rm fg}$. The stack for \ion{C}{4}, which include line-of-sight 
absorbers at all distances, shows a large, blueshifted mean velocity field.
}
\label{fig:stacks_fg}
\end{figure}

\subsection{Significance of the asymmetric absorption}
\label{sec:significance_+ve}

Given the small sample size, one must scrutinize the statistical significance of the measured 
velocity offsets. To assess the statistical significance, we perform a boostrap analysis by 
randomly sampling from the full sample 10000 times. We measure the flux-weighted centroid of each 
bootstrap realization, and quote the standard deviation in the bootstrap realizations to be the 
scatter in the centroid of the data. The scatters $\approx100\,{\rm \,s^{-1}}$ are comparable 
to the measured offsets, indicating large intrinsic variation in quasar CGM environments (see 
also QPQ8). Given the large intrinsic scatter, we do not attempt to explore whether there exists 
relative asymmetry between \ion{C}{2} and \ion{C}{4} absorption due to different ionization 
potentials.

One may also ask whether the measured positive offsets come from systematic bias in redshift 
measurements due to the Baldwin effect \citep{Baldwin77}. \cite{Shen16} reported that, the 
[\ion{O}{3}] emission of $z\sim2$ quasars is more asymmetric and weaker than that in typically 
less luminous low-$z$ quasars. To test for this potential source of bias, we create another mean 
stack at \ion{C}{2}\,1334 by replacing the [\ion{O}{3}] redshifts by a \ion{Mg}{2}, H$\alpha$, or 
H$\beta$ redshift. We are able to replace for 13 out of the 14 systems with [\ion{O}{3}] redshifts 
in the original sample. The new stack is similiar in velocity structure and again shows a positive 
offset. We thus conclude that our algorithm for measuring redshifts is not severely biased by 
the blue wing of the [\ion{O}{3}] emission-line.

We also generate a mean-stacked spectrum for \ion{Mg}{2}\,2796 for lower redshift quasar pairs, 
using the same selection criteria as the main QPQ9 sample. The quasar pairs are selected from the 
igmspec database, with $z_{\rm fg}$ measured by \cite{HewettWild10}. There are 231 pairs selected, 
with a median $z_{\rm fg}$ of 0.90 and a median $R_\perp$ of 208\,kpc. We present the mean and 
median stacks in Figure~\ref{fig:stack_z1}. The absorption is weaker than the $z\sim2$ main QPQ9 
sample. Gaussian absorption models fitted to the stack recover a centroid of 
$47\pm122\,{\rm km\,s^{-1}}$ and a dispersion of $119\,{\rm km\,s^{-1}}$. The offsets from 
$0\,{\rm km\,s^{-1}}$ are smaller than the offsets in the $z\sim2$ sample.

Since the large scatters in the centroids represent intrinsic variation rather than redshift 
errors, and the \ion{Mg}{2} stack for lower redshift does not suggest a similar offset, the hint 
of asymmetry cannot be ignored. In the Discussion section, we discuss two possible explanations 
for the asymmetry.

%Indeed, a small offset $mdv < 10 kms$ may be expected even with large samples.

\subsection{Significance of the large velocity fields}
\label{sec:significance_width}

\begin{figure}
\includegraphics[width=2.5in]{Figures/fig_monte.pdf}
%\includegraphics[width=2.5in]{f07.pdf}
\caption{The same \ion{C}{2} mean stack shown in the first panel of 
Figure~\ref{fig:stacks_and_fits} is shown in thick, black, and the Gaussian absorption model to 
the data is shown in thin, blue. In thin, green, we overplot the Gaussian absorption model of the 
Monte Carlo simulations generated from a purely clustering argument. The model from clustering 
analysis is multiplied to the pseudo-continuum level of the stack of the observational data, 
shifted to the centroid of the stack of the data, and broadened by the mean redshift error in the 
data. The model has a smaller dispersion than the data by two times the modeling error.
}
\label{fig:monte}
\end{figure}

>>>>

\title{Quasars Probing Quasars IX. The Kinematics of the Circumgalactic Medium Surrounding 
$z\sim2$ Quasars [v1.4]}

@@

\begin{abstract}
We examine the kinematics of the gas in the environments of massive galaxies hosting quasars at 
$z\sim2$. We employ 112 projected quasar pairs to study the circumgalactic gas of the foreground 
quasars in absorption. The foreground quasars have precise redshift measurements, using 
emission-lines with uncertainty $\lesssim300\,{\rm km\,s^{-1}}$ and average offsets from the 
systemic redshift $\lesssim|100\,{\rm km\,s^{-1}}|$. We stack the background quasar spectra at the 
foreground quasar's systemic redshift. The mean absorption in \ion{C}{2}, \ion{C}{4}, and \ion{Mg}{2} show large velocity widths, and have velocity 
centroids that show a small positive offset relative to the systemic. We argue that a possible 
explanation to the observed velocity fields is outflowing gas combined with anisotropic or 
intermittent ionizing radiation of the quasars. 
\end{abstract}

@@

\section{Introduction}
\label{sec:introduction}

Galaxy formation and evolution are driven by the flows of gas into and out of their interstellar 
medium. Current theories demand that star-forming galaxies maintain these flows. Gas accretes, 
cools, and adds to the fuel supply, while star formation feedback heats gas, blows it out of 
galaxies, and regulates star formation \citep[for a review see][]{SomervilleDave15}.

Direct observations of galactic flows are difficult to acquire. Detecting the presence of 
the gas is itself challenging. Either the gas mass is too small, or the gas density is too low for 
the detection of line-emission, e.g.\ 21\,cm, Ly$\alpha$, or H$\alpha$ from \ion{H}{1}. Resolving 
the kinematics and establishing the mass flux pose an even greater challenge. These challenges are 
accentuated for distant, young galaxies, where flows of gas are predicted to prevail 
\citep{Keres+09,Fumagalli+11}. Therefore, with rare exceptions, 
\citep[e.g.][]{Cantalupo+14,Hennawi+15}, the community has relied on absorption-line spectroscopy 
to detect and characterize the gas surrounding galaxies 
\citep[e.g.][]{BergeronBoisse91,Steidel+10,Prochaska+11,Tumlinson+13}. 
In a previous paper of the Qussars Probing Quasars series\citep[][QPQ8]{QPQ8}, we 
measured the velocity field for \ion{C}{2}\,1334 and \ion{C}{4}\,1548, finding that the 
circumgalactic medium frequently exhibits large velocity widths that are offset from the systemic 
redshift. The offsets, $\delta v$, are often positive, with the sign convention that positive 
velocities indicate a redshift from the systemic. From a sample of 7 \ion{C}{2} systems and 10 
\ion{C}{4} systems, we measured the velocity interval that encompasses 90\% of the total optical 
depth, $\Delta v_{90}$, and the $1\sigma$ dispersion relative to the profile centroid, $\sigma_v$. 
The median $\Delta v_{90}$ is $555\,{\rm km\,s^{-1}}$ for \ion{C}{2}\,1334 and is 
$342\,{\rm km\,s^{-1}}$ for \ion{C}{4}\,1548. The median $\sigma_v$ is $249\,{\rm km\,s^{-1}}$ for 
\ion{C}{2}\,1334 and is $495\,{\rm km\,s^{-1}}$ for \ion{C}{4}\,1548. These velocity fields exceed 
all previous measurements from galaxies and/or absorption systems at any epoch.

With absorption-line spectroscopy of background sightlines, other researchers also have had 
success in characterizing the flows of gas around galaxies. \cite{Rakic+12} found a net 
large-scale inflow around star-forming galaxies, or a Kaiser effect for gas on on 
1\textendash2\,Mpc scales. \cite{Johnson+15} studied the CGM surrounding $z\sim1$ quasars, and 
found large peculiar motions in the gas exceeding the expected virial velocity, which they 
interpret as quasar-driven outflows. However, the velocity spreads were not well quantified. Other 
existing studies that found large velocity spreads are limited to single sightlines with most of 
the gas within several hundred ${\rm km\,s^{-1}}$ \citep[e.g., ][]{Tripp+11}, or with gas tracing 
a higher ionization state than the QPQ absorption systems\citep[e.g., ][]{Churchill+12}, or where 
the average velocity spread is smaller than that measured in QPQ8 
\citep[e.g., ][]{Gauthier13,Muzahid+15,Zahedy+16}.

A significant limitation of absorption-line analysis of transverse sightlines, especially 
regarding galactic-scale flows, is the inherent symmetry of the experiment. One generally lacks 
any constraint on the distance of the gas along the sightline. Positive or negative velocities 
with respect to the galaxy may be interpreted as gas flowing either toward or away from the 
system. ``Down-the-barrel'' observations break this symmetry, and have generally provided evidence 
for flows away from galaxies \citep{Rupke+05,Martin05,Weiner+09,Rubin+14}. However, these data are 
frequently at low spectral resolution which limits one's sensitivity to inflowing gas.

In this paper (hereafter QPQ9), we examine the flows of gas in the environments of massive 
galaxies hosting quasars. Our approach leverages a large dataset of quasar pairs 
\citep[][QPQ1]{QPQ1} to use the standard technique of absorption-line spectroscopy with background 
quasars. These quasar pairs 
have angular separations that correspond to less than 300\,kpc projected separation at the 
foreground quasar's redshift. Our previous publications from these quasar pairs have established 
that these galaxies are surrounded by a massive, cool, and enriched CGM 
\citep[QPQ5, QPQ6, QPQ7:][]{QPQ5,QPQ6,QPQ7}. We have collected a sample of 112 background 
spectra that are paired with foreground quasars with precisely measured redshifts. 
Among the sightlines in the QPQ9 sample, 13 have spectral resolution $> 5000$ from echellette or 
echelle observations, and have been analyzed separately in QPQ8. Our primary 
scientific interests are twofold: (i) search for signatures of galactic-scale outflows from the 
central galaxy, presumably driven by recent star formation and/or active galactic nuclei feedback; 
(ii) characterize the dynamics of flows of gas around these massive system. We further describe 
an aspect of this experiment that offers a unique opportunity to study galactic-scale flows: we 
argue that, the anisotropic or intermittent radiation of the foreground quasars may break the 
symmetry in the velocity field of circumgalactic absorbers. If the ionizing radiation field is 
asymmetric, the absorbers may also distribute asymmetrically. Alternatively, finite quasar 
lifetime will result in different radiation fields impinged on the gas closer to versus 
further away from the background quasar, due to different light travel times.

@@

From our QPQ survey\footnote{http://www.qpqsurvey.org}, we have analyzed a subset of systems that 
pass within transverse separation $R_\perp<300$\,kpc from a foreground quasar with 
$z_{\rm fg} > 1.6$. We restrict the sample to foreground quasars with redshift measured from 
\ion{Mg}{2}\,2800, [\ion{O}{3}]\,5007, or H$\alpha$ emission, giving a precision of 
$300\,{\rm km\,s^{-1}}$ or better and an average offset from the systemic redshift of 
$|100\,{\rm km\,s^{-1}}|$ or less. According to \citep{Shen+16}, the [\ion{O}{3}] emission-line 
redshifts have the smallest total scatter (due to intrinsic scatter and measurement error) of 
$68\,{\rm km\,s^{-1}}$ about the systemic redshift, and we analyze the sub-sample with 
[\ion{O}{3}] redshifts separately. The [\ion{O}{3}] line has an average blueshift of 
$48\,{\rm km\,s^{-1}}$ about the systemic redshift, which has been added when we compute the 
redshift of the line. The scatter and average offset of [\ion{O}{3}] redshifts reported by 
\cite{Shen+16} is consistent with the numbers reported by \cite{Boroson05} using a larger but 
lower redshift sample. Systemic redshifts measured from \ion{Mg}{2} have a precision of 
$226\,{\rm km\,s^{-1}}$ according to \cite{Shen+16}, and we have taken into account their 
reported median blueshift of $57\,{\rm km\,s^{-1}}$ of \ion{Mg}{2} from the systemic. We note that 
\cite{Richards+02} reported a median redshift of $97\,{\rm km\,s^{-1}}$ of \ion{Mg}{2} from 
[\ion{O}{3}] using a larger but lower redshift sample. In QPQ8 \citep{QPQ8}, we quantified 
the precision of H$\alpha$ to be $300\,{\rm km\,s^{-1}}$ and the median offset from the systemic 
redshift is close to zero, consistent with the velocity shifts measured by \cite{Shen+11}. 
Although H$\beta$ is a narrow emission-line, we do not consider its redshift sufficiently reliable 
for use as systemic redshift. H$\beta$ redshifts have a large scatter about the systemic 
$\approx400\,{\rm km\,s^{-1}}$, and a large average offset about the systemic 
$\approx100\,{\rm km\,s^{-1}}$ \citep[][; QPQ8]{Shen+16}. 
We further add to the QPQ dataset with quasar pairs selected from the public dataset of 
igmspec\footnote{https://github.com/specdb/igmspec}, which includes the spectra from the quasar 
catalogs based upon the Sloan Digital Sky Survey Seventh Data Release \citep{Schneider+10} and the 
Twelfth Data Release \citep{Paris+17}. We only select pairs with $z_{\rm fg}$ measured by 
\cite{HewettWild10} using the \ion{Mg}{2}\,2800 emission-line, and we add the median blueshift of 
\ion{Mg}{2} from the systemic to these redshifts. We reached a final sample size of 112. 
Figure~\ref{fig:experiment} summarizes the experimental design. We refer the reader to previous 
QPQ publications for the details on the redshift centroiding algorithm, data reduction, and 
continuum normalization (QPQ6; QPQ8).

@@

Table~\ref{tab:sample} lists the full QPQ9 sample. In Table~\ref{tab:summary}, we first list the 
sample size, the median $z_{\rm fg}$, and the median $R_\perp$ of the quasar pairs that survive 
the above selection criteria for \ion{C}{2}\,1334, \ion{C}{4}\,1548, and \ion{Mg}{2}\,2796 
respectively. We then provide the summary for the sub-sample with $z_{\rm fg}$ measured from 
[\ion{O}{3}].

@@

\subsection{Stacked Profiles}
\label{sec:stacks}

@@

We create composite spectra that average over the intrinsic scatter in quasar environments, 
continuum placement errors, and redshift errors. The individual spectra of background quasars are 
shifted to the rest-frame of the foreground quasars at the transitions of interest. Each spectrum 
has been linearly interpolated onto a fixed velocity grid centered at $z_{\rm fg}$ with bins of 
$100\,{\rm km\,s^{-1}}$. For a velocity bin of this size, it is unnecessary to smooth the data to 
a common spectral resolution. The individual spectra are then combined with a mean or a median 
statistic. Bad pixels in the individual spectra have been masked before generating the 
composites. Since each quasar pair gives an independent probe of the CGM, each pair has an equal 
weighting in the stacked profiles, i.e.\ we do not weight the spectra by the measured S/N near the 
metal ion transitions. Scatter in the stacked spectra is dominated by randomness in the CGM rather 
than scatter in the flux of individual observations. The mean statistic of the individual spectra 
yields a good estimate of the average absorption and preserves equivalent width. The median 
statistic is less sensitive to outliers, however the averaged equivalent width is smaller and the 
analysis on the velocity field becomes more uncertain. In the following we present stacked spectra 
using both the mean and the median statistic.

In Figure~\ref{fig:stacks_and_fits}, we present mean and median stacks of \ion{C}{2}\,1334, 
\ion{C}{4}\,1548, and \ion{Mg}{2}\,2796 absorption of the QPQ9 sample. We focus on the 
analysis results of the \ion{C}{2} mean stack. \ion{C}{4} and \ion{Mg}{2} are doublet transitions 
and it is more challenging to interpret their kinematics.
%To assess the average absorption of these transitions,
%we have combined the data with a novel technique.
%We have fitted the combined dataset using a cubic b-spline
%with knots at every 100\,kms.  We weighted each data
%point by the velocity width of the pixel to insure that 
%each sightline makes an equal contribution to the stack.
%These b-spline profiles are presented in the figure
%and a trivial integration gives the reported equivalent
%widths.
%[consider down-weighting systems with $<3\sigma$ EW]
%[Comnent on EW from 'standard' technique]
Two results are evident in Figure~\ref{fig:stacks_and_fits}: (i) the mean \ion{C}{2} stack 
exhibits excess absorption spanning a large velocity width; (ii) the mean absorption is likely 
skewed toward positive velocities. To model the absorption, we introduce a Gaussian profile while 
allowing a constant pseudo-continuum level to vary. We perform $\chi^2$ minimization with each 
channel given equal weight. From the best-fit to the data, we measure the centroid of the 
\ion{C}{2} stack to be $+208\,{\rm km\,s^{-1}}$ and the $1\sigma$ dispersion to be 
$312\,{\rm km\,s^{-1}}$. The centroid suggests an asymmetry that contradicts the standard 
expectation, while the dispersion suggests extreme kinematics. The median stack, on the other 
hand, shows weaker absorption, and the Gaussian model has a centroid closer to zero.

We also create mean and median stack for the sub-sample with [\ion{O}{3}] redshifts and model the 
absorption with Gaussian best-fit. The \ion{C}{2} mean stack for this sub-sample has a centroid at 
$+239\,{\rm km\,s^{-1}}$, and a dispersion of $349\,{\rm km\,s^{-1}}$, consistent with the full 
sample.

@@

The above analyses are summarized in Table~\ref{tab:summary}. The 
Gaussian models normalized to pseudo-continuum are overplotted on the data stacks in 
Figure~\ref{fig:stacks_and_fits}.

\input{Tables/tab_summary.tex}
%\input{tab_summary.tex}

\begin{figure}
\subsection{Interpretation of the asymmetric absorption}
\label{sec:significance_+ve}

\includegraphics[width=2.5in]{Figures/fig_histogram_cen.pdf}
%\includegraphics[width=2.5in]{f03.pdf}
\caption{Histogram of the absorption centroids of 10000 bootstrap realizations of the data sample 
for the \ion{C}{2} mean stack. 98\% of the centroids are positively offset from $z_{\rm fg}$.}
\label{fig:histogram_cen}
\end{figure}

\begin{figure}
\includegraphics[width=2.5in]{Figures/fig_stack_z1.pdf}
%\includegraphics[width=2.5in]{f04.pdf}
\caption{Mean stack at \ion{Mg}{2}\,2796, for a lower redshift sample of quasar pairs at 
$z\sim0.9$. Line-style coding is the same as in Figure~\ref{fig:stacks_and_fits}. The centroid is 
approximately $0\,{\rm \,km\,s^{-1}}$, and the absorption is weaker than the main QPQ9 sample. 
}
\label{fig:stack_z1}
\end{figure}

Given the small sample size, one must scrutinize the statistical significance of the measured 
velocity offsets. To assess the statistical significance, we perform a boostrap analysis by 
randomly sampling from the full sample 10000 times. We introduce a Gaussian absorption profile to 
model each bootstrap realization, and quote the standard deviation in the the bootstrap 
realizations to be the scatter in the centroid of the data. The scatters 
$\approx100\,{\rm km\,s^{-1}}$ are comparable to the measured offsets, indicating large intrinsic 
variation in quasar CGM environments (see also QPQ8). In Figure~\ref{fig:histogram_cen}, we show 
the distribution of the absorption centroids of the bootstrap realizations. We find that 98\% of 
the centroids are at positive velocities. We place a generous $3\sigma$ upper limit to the small 
offset of the centroid from $z_{\rm fg}$ for the \ion{C}{2} mean absorption at 
$\delta v<+451\,{\rm km\,s^{-1}}$. Given the large intrinsic scatter, we do not attempt to explore 
whether there exists relative asymmetry between \ion{C}{2} and \ion{C}{4} absorption due to 
different ionization potentials.

One may also ask whether the measured positive offsets come from systematic bias in redshift 
measurements due to the Baldwin effect \citep{Baldwin77}. \cite{Shen16} reported that, the 
[\ion{O}{3}] emission of $z\sim2$ quasars is more asymmetric and weaker than that in typically 
less luminous low-$z$ quasars. To test for this potential source of bias, we create another mean 
stack at \ion{C}{2}\,1334 by replacing the [\ion{O}{3}] redshifts by a \ion{Mg}{2} or H$\alpha$ 
redshift when available. We are able to replace for 8 out of the 14 systems with [\ion{O}{3}] 
redshifts in the original sample. The new stack is similiar in velocity structure and again shows 
a positive offset $\approx+240\,{\rm km\,s^{-1}}$. We thus conclude that our algorithm for 
measuring redshifts is not severely biased by the blue wing of the [\ion{O}{3}] emission-line.

Motivated by the study of \ion{Mg}{2} absorbers surrounding $z\sim1$ quasars by \cite{Johnson+15}, 
we also generate a mean-stacked spectrum for \ion{Mg}{2}\,2796 for lower redshift quasar pairs.  
We select quasars with $0.4<z_{\rm fg}<1.6$ and use the same other selection criteria as the main 
QPQ9 sample. The quasar pairs are selected from the igmspec database, with $z_{\rm fg}$ measured 
by \cite{HewettWild10}. For quasars with $z_{\rm fg}<0.84$, as redshift determination is dominated 
by [\ion{O}{3}] emission, a shift of $+48\,{\rm km\,s^{-1}}$ is applied to bring the emission-line 
redshift to the systemic. For quasars with $0.84<z_{\rm fg}<1.6$, as redshift determination is 
dominated by \ion{Mg}{2} emission, a shift of $57\,{\rm km\,s^{-1}}$ is applied. There are 231 
pairs selected, with a median $z_{\rm fg}$ of 0.90 and a median $R_\perp$ of 208\,kpc. We present 
the mean tack in Figure~\ref{fig:stack_z1}. The absorption is weaker than the $z\sim2$ main QPQ9 
sample. Gaussian absorption models fitted to the stack recover a centroid of 
$-13\pm410\,{\rm km\,s^{-1}}$ and a dispersion of $155\,{\rm km\,s^{-1}}$. The average offset 
from $0\,{\rm km\,s^{-1}}$ is smaller than the offsets in the $z\sim2$ sample.

Since the large scatter in the centroids represent intrinsic variation rather than redshift 
errors, and the \ion{Mg}{2} stack for lower redshift does not suggest a similar offset, we 
consider that the asymmetry signal in the $z\sim2$ sample is likely to be real. In the Discussion 
section, we discuss two possible explanations for the asymmetry.

\subsection{Interpretation of the large velocity fields}
\label{sec:significance_width}

\begin{figure}
\includegraphics[width=2.5in]{Figures/fig_monte.pdf}
%\includegraphics[width=2.5in]{f05.pdf}
\caption{The same \ion{C}{2} mean stack shown in the first panel of 
Figure~\ref{fig:stacks_and_fits} is shown in thick, black. In thin, green, we overplot the 
Gaussian absorption model of the Monte Carlo simulations generated from a purely clustering 
argument. The model from clustering analysis is multiplied to the pseudo-continuum level of the 
stack of the observational data, shifted to the centroid of the stack of the data, and broadened 
by the mean redshift error in the data. The model is a good description of the data, with a 
dispersion within modeling error of the dispersion in the data. We overplot in dashed, yellow an 
absorption profile with $\sigma_v=658\,{\rm km\,s^{-1}}$. Motions that produce this width are 
ruled out at $3\sigma$ confidence by bootstrap analysis on the observational data. 
}
\label{fig:monte}
\end{figure}
